Economic Evaluation of Mis-speficied Geographically Weighted Regression Models for Site-specific Nitrogen Management

### 2023-11-05 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_2.rmd

+ <span style = "color: blue;"> P. 10, line 199: In this sentence, you should mention which specific statistical distribution the error term follows, despite the fact that you mention Gaussian random fields below. </span>

Response: It follows a normal distribution in a way it is spatially correlated. This has been made clear in the manuscript (see page ??, line ??).

+ <span style = "color: blue;">P. 12, line 212: It would be useful to add a footnote here explaining why the range of 600m was chosen.</span>

Response: We added an explanation that the 600m range was chosen based on empirical data of our existing on-farm trials (see page ??, lines ??).

@@

+ <span style = "color: blue;">P. 14, line 254: For additional clarity, you could point out that the EONR rate is just the value of N that solves $\\cdot f(N) - \omega\dcot N$, where $f(N)$ is SCAM-estimated. </span>

Response:

+ <span style = "color: blue;"> P. 15, lines 277-279: Add a sentence (perhaps in a footnote) mentioning how this shape constraint is actually imposed. </span>

Response: Expalining how the shape constraint is imposed would take more than a page of mathematical explanations. We added a footnote that  cites Pya's journal article titled "Shape constrained additive models" published in Statistics and computing.

@@

+ <span style = "color: blue;">PP. 22-23, lines 439-441: This sentence should be removed because it seems speculative. More importantly, researchers do not "have" to implement a methodology because it is conveniently available in standard software; instead, they could code their own models, methods, etc.  </span>

Response: There is no speculation in this sentence. We are stating a drawback of linear-plateau model. What we state is a irrefutable fact and important in real world practice of estimating yield response function.

@@

+ <span style = "color: blue;">P. 33, Figure 2: In the notes to this figure, you should add that the 1,440 subplots are illustrated as 24 rows x 12 columns, each containing 5 subplots (24 x 12 x 5 = 1,440). Also add that there are 72 rows x 120 columns of cells (72 x 120 = 8,640).  </span>

Response:

Writing

+ <span style = "color: blue;">P. 4, line 45: Replace "dramatic" with "seemingly implausibly large"</span>

Response: We followed your suggestion.

+ <span style = "color: blue;">P. 4, line 54: Replace "suspect" with "hypothesize". Same comment for "suspect" on P. 9, line 153</span>

Response: We followed your suggestion.

+ <span style = "color: blue;">P. 5, line 77: You do not need to write (OFPE) again here since you have already introduced
the acronym.</span>

Response: We followed your suggestion.

+ <span style = "color: blue;">P. 8, line 124: You should place the first instance of "(EONR)" here after "economically
optimal nitrogen rates" rather than line 132.</span>

Response: We followed your suggestion.

+ <span style = "color: blue;">P. 8, line 130: Replace "dangerous" with "problematic" Same comment for P. 22, line 438 </span>

Response: We followed your suggestion.

@@

+ P. 13, line 233: Replace "due the" with "due to the"

Response: We followed your suggestion.

+ P. 14, line 262: This is the first and only mention in the paper of a benchmark. Given that,
what is a "lower" benchmark?

Response: We have changed the wording to "In this scenario."

@@

+ P. 19, line 269: Replace "truea" with "true"

Response: We followed your suggestion.

+ P. 22, line 453: Remove the word "please"

Response: We followed your suggestion.

+ P. 24, lines 468-474: Remove the clause "After the development of software that..."
Additionally, you should add quotation marks to both instances of "pure" in this paragraph.

Response: We followed your suggestion.

### 2023-11-05 Writing/manuscript_gwr.rmd
more replies added

The spatial distributions of cell-level parameters $\alpha_{j, i}$, $\beta_{j, i}$, $\gamma_{j,i}$, $\tau_{j, i}$, and the error term $\varepsilon_{j, i}$ were simulated by generating spatially correlated random fields using unconditional Gaussian geostatistical simulation based on the specified variograms [@dietrich1996fast; @wood1994simulation]. The simulation processes were conducted using the R package gstat [@graler16]. Specifically, the model is spherical, the nugget variance is zero, and the range is 600 meters. The nugget value of zero means that infinitesimally close observations have a zero covariance (i.e., they are identical). The range of 600m means that observations separated by more than 600m are spatially uncorrelated. A higher range value indicates increased spatial dependence, meaning that less abrupt differences tend to be observed between the production function parameters of neighboring cells. The mean and sill variance of each parameter were specified to result in a realistic mean yield of $11,416$ kg ha$^{-1}$, and such that the cells' true economically optimal N rates ranged from $113$ kg ha$^{-1}$ to $273$ kg ha$^{-1}$ across all the simulations, a range into which most real-world N rate recommendations fall [e.g., @sawyer2018]. Note that the range of the optimal N rates of individual rounds of simulations are narrower. In defining the magnitude of the error term, we utilized the experimental data generated through eight on-farm randomized N field trials conducted by the Data-Intensive Farm Management Project (DIFM) project in 2018 [@bullock2019data]. Using the data from each of the eight actual trials, separate regressions of yield on N were run, and standard deviations of the residuals were calculated. The mean value of the eight standard deviations was $1370$ kg ha$^{-1}$, which was the square root value of the sill variances assigned to the simulations' error terms.

@@

where $g_k(\cdot)$ is the $k$th spline basis and $\beta_k$ is its coefficient to be estimated. The $\beta_k$s were constrained such that the resulting relationship between $y_j$ and $N_j$ is such that $y_j$ monotonically increases with $N_j$, but at a diminishing rate.

>>>>

The spatial distributions of cell-level parameters $\alpha_{j, i}$, $\beta_{j, i}$, $\gamma_{j,i}$, $\tau_{j, i}$, and the error term $\varepsilon_{j, i}$ were simulated by generating spatially correlated random fields using unconditional Gaussian geostatistical simulation based on the specified variograms [@dietrich1996fast; @wood1994simulation]. The simulation processes were conducted using the R package gstat [@graler16]. Specifically, the model is spherical, the nugget variance is zero, and the range is 600 meters. The nugget value of zero means that infinitesimally close observations have a zero covariance (i.e., they are identical). The range of 600m means that observations separated by more than 600m are spatially uncorrelated. A higher range value indicates increased spatial dependence, meaning that less abrupt differences tend to be observed between the production function parameters of neighboring cells. The choice of 600m range in this study was based on empirical data generated through eight on-farm randomized N field trials conducted by the Data-Intensive Farm Management Project (DIFM) project in 2018 [@bullock2019data]. The mean and sill variance of each parameter were specified to result in a realistic mean yield of $11,416$ kg ha$^{-1}$, and such that the cells' true economically optimal N rates ranged from $113$ kg ha$^{-1}$ to $273$ kg ha$^{-1}$ across all the simulations, a range into which most real-world N rate recommendations fall [e.g., @sawyer2018]. Note that the range of the optimal N rates of individual rounds of simulations are narrower. The magnitude of the error term $\varepsilon_{j, i}$ was also based on the DIFM project empirical data. Using the data from each of the eight actual trials, separate regressions of yield on N were run, and standard deviations of the residuals were calculated. The mean value of the eight standard deviations was $1370$ kg ha$^{-1}$, which was the square root value of the sill variances assigned to the simulations' error terms.

@@

where $g_k(\cdot)$ is the $k$th spline basis and $\beta_k$ is its coefficient to be estimated. The $\beta_k$s were constrained such that the resulting relationship between $y_j$ and $N_j$ is such that $y_j$ monotonically increases with $N_j$, but at a diminishing rate^[Please see @pya2015shape for technical details on how to implement this constraint under the GAM framework.].
